---
title: "Stock Market Prediction using Numerical Analysis"
author: "Aditya Dawn"
date: "19/02/2021"
runtime: shiny
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## **Import Data**  
Here, we are importing the stock history of Apple.
```{r echo=TRUE, message=FALSE, warning=FALSE}
library(tidyquant)
```
```{r echo=TRUE, message=FALSE, warning=FALSE}
getSymbols("AAPL",
           from = "2001-01-01",
           to = "2020-06-30")
prices <- tq_get("AAPL",
                 from = "2001-01-01",
                 to = "2020-06-30",
                 get = "stock.prices")
```
## **Primary Visualization**  

```{r echo=TRUE, message=FALSE, warning=FALSE}
library(plotly)
p <- prices %>%
      ggplot(aes(x = date, y = adjusted, color = symbol)) +
      geom_line()
ggplotly(p)
```

Now, let us analyze the stock history of Apple.  



## **Making of Dataframe**  
```{r echo=TRUE, message=FALSE, warning=FALSE}
aapl <- as.data.frame(AAPL)
aapl <- cbind(Date = rownames(aapl), aapl)
rownames(aapl) <- 1:nrow(aapl)
```


## **Numerical Aalysis**  

```{r echo=TRUE, message=FALSE, warning=FALSE}
library(tseries)
```

## **Preprocessing of the data**

### **Stationarity of the data**  

For testing of Stationarity of the stock history, let us consider that :
$H_0 : Not Stationary$ vs $H_1 : Staionary$
```{r echo=TRUE, message=TRUE, warning=FALSE}
adf.test(aapl$AAPL.Close,alternative ="stationary")
```
The p-value of ADF test is 0.99, which is greater than 0.05. In this case, we fail to reject the null hypothesis. Therefore the data isn't stationary.

```{r echo=TRUE, message=TRUE, warning=FALSE}
kpss.test(aapl$AAPL.Close, null = "Trend")
```
In case of KPSS test, p-value is less than 0.05. In this case, we reject null hypothesis. That means the data isn't stationary. 

### **Removal of Stationarity of the data**  
Let's check the first level differencing.  

```{r echo=TRUE, warning=FALSE}
aapl_Close <- diff(aapl$AAPL.Close)
adf.test(aapl_Close, alternative = "stationary")
kpss.test(aapl_Close, null = "Trend")
```
ADF test has p-value of 0.01 (less than 0.05). Therefore, we reject the null hypothesis. This means the first differenced data is stationary.
KPSS test has p-value of 0.06833 (greater than 0.05). This means we fail to reject null hypothesis. Therefore, the first differenced data is stationary.  

Data has become stationary after first differencing. However, there is seasonal trend. We need to adjust that. 

### **Seasonality of the data**  
```{r echo=TRUE, warning=FALSE}
aapl_Close <- diff(aapl_Close)
adf.test(aapl_Close, alternative = "stationary")
kpss.test(aapl_Close,null="Trend")
```

Here both test suggests the stationarity of data. 



Let’s analyse the ACF and PACF.
```{r echo=TRUE, message=FALSE, warning=FALSE}
library(forecast)
```
```{r echo=TRUE, message=FALSE, warning=FALSE}
ggtsdisplay(aapl_Close, lag.max = 12, xlab=" Years 2001-2020", ylab="AAPL.Close", main="Seasonally Adjusted Close Values")
```

Clearly, here are not significant points in PACF. While in case of ACF, probable significant points are at lags 2, 5, 7, 9 and 12.

## **ARIMA Model**  

First, let us create the training set.
```{r echo=TRUE, message=FALSE, warning=FALSE}
library(caTools)
aapl_train <- aapl_Close[1:3920]
```

### **Best ARIMA Model**
Now, lets find the best ARIMA model on the training set.

```{r echo=TRUE, message=TRUE, warning=FALSE}
aapl_arm_best <- auto.arima(aapl_train, stationary = TRUE, trace=TRUE)
```


```{r echo=TRUE, message=TRUE}
summary(aapl_arm_best)
```

Now, let us analyze the Best ARIMA Model.
```{r echo=TRUE, message=FALSE, warning=FALSE}
checkresiduals(aapl_arm_best)
```

Clearly, the p-value of the Ljug-Box test suggests that, this model is statistically significant.


Now, let us fit the data on the training set.
```{r echo=TRUE, message=TRUE}
aapl_arima <- arima(aapl_train, order = c(5, 0, 0))
summary(aapl_arima)
```
## **Forecasting with the model on the Apple Stock History**  
```{r echo=TRUE}
aapl_forecast <- forecast(aapl_arima, h = 100)
plot(aapl_forecast)
```


**The Blue part in the above image shows the forecast made by the model.**

  
  
  
  
# **THANK YOU!**





